Numerical simulations of the Cordilleran ice sheet through the last glacial cycle

### 2014-07-18 cordillera-cycle.tex
Add section 4.1.2.

\todo{Add MIS~2 ice topo and velocity map. Include two paragraphs from Martin.
      Describe model limitations referring to \citet{Seguinot.etal.2014}}

@@

>>>>

During maximum glaciation, the main meridional ice divide is positioned over
the western flank of the Rocky Mountains (Fig.~\ref{fig:snapshots}, lower
panels; Fig.~\ref{fig:mis2}). This result appears to contrast with
palaeoglaciological reconstructions for central and southern British Columbia
that inferred the ice divide to have been situated in a more westerly position,
over the western margin of the Interior Plateau \citep{Ryder.etal.1991,
Stumpf.etal.2000, Kleman.etal.2010, Clague.Ward.2011, Margold.etal.2013a}. A
latitudinal saddle has been inferred to have connected ice dispersal centres in
the Columbia Mountains with the main ice divide \citep{Ryder.etal.1991,
Kleman.etal.2010, Clague.Ward.2011, Margold.etal.2013a}. A latitudinal saddle
does indeed features in our modelling results, however, in an inverse
configuration between the main ice divide over the Columbia Mountains and a
secondary divide over the southern Coast Mountains (Fig.~\ref{fig:mis2}).

On the one hand, this could reflect the fact that our model does not include
feedback mechanisms between ice sheet topography and the regional climate.
Firstly, during the build-up phase preceding the LGM, rapid accumulation over
the Coast Mountains enhanced the topographic barrier formed by these mountain
ranges, which likely resulted in a decrease of precipitation and, therefore,
accumulation in the interior. Secondly, latent warming of the moisture-depleted
air parcels flowing over this enhanced topography could have resulted in an
inflow of warmer air over the eastern flank of the ice sheet, increasing melt
along the advancing margin \citep[cf.][]{Langen.etal.2012}. Because these two
processes, both inhibiting of ice-sheet growth, are absent from our model, the
eastern margin of the ice sheet and the position of the main meridional ice
divide are certainly biased towards the east in our simulations
\citep{Seguinot.etal.2014}.

On the other hand, field-based palaeoglaciological reconstructions have
struggled to reconcile the more westerly-centred ice divide in south-central
British Columbia with evidence in the Rocky Mountains and beyond, that the
Cordilleran ice sheet invaded the western Interior Plains, where it merged with
the southwestern margin of the Laurentide ice sheet and was deflected to the
south \citep{Jackson.etal.1997, Bednarski.Smith.2007, Kleman.etal.2010,
Margold.etal.2013, Margold.etal.2013a}. Ice geometries from our model runs do
not have this problem, because the position and elevation of the ice divide
results in significant ice drainage across the Rocky Mountains at the LGM
(Fig.~\ref{fig:mis2}).

@@

(Fig.~\ref{fig:snapshots}, upper panels; Fig.~\ref{fig:mis4})
(Fig.~\ref{fig:mis4})
